Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-20 ms/main.tex
Add alpha vs v graphs to the main file

\begin{corollary}[Intermediate association of transmission and cooperation]
Cooperation will increase from rarity if social association is high enough, or specifically if
  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
    \begin{aligned}
    T_A > T_B &\;\; \text{and} \;\; a_2 < \alpha, \quad \text{or} \\
    T_A < T_B &\;\; \text{and} \;\; a_1 < \alpha \,.
    \end{aligned}
    \end{equation} 
\end{corollary}

@@

\end{result}
These conditions are illustrated in \autoref{fig:result3}.

@@

In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
\\
\begin{corollary}[Necessity condition for fixation of cooperation.]
  Fixation of cooperation is possible only when
  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
    \begin{aligned}
      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
    \end{aligned}
    \end{equation} 
\end{corollary}
When there is horizontal transmission bias for cooperation, fixation can occured for every value of vertical transmission because $\hat{v}<0$.
However, if the the horizontal bias favours defection, for fixation of cooperation to occur the vertical transmission must be higer than $\hat{v}$.

@@

\begin{figure}[htb]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
    The vertical transmission rate $v$ is on the x-axis.
    Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines. 
    (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
    \label{fig:result3}
\end{figure}

>>>>

\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
Cooperation will increase from rarity if social association is high enough, or specifically if
  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
    \begin{aligned}
    T_A > T_B &\;\; \text{and} \;\; a_2 < \alpha, \quad \text{or} \\
    T_A < T_B &\;\; \text{and} \;\; a_1 < \alpha \,.
    \end{aligned}
    \end{equation} 
\end{corollary}

@@

\end{result}
These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b.

@@

In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
\\
\begin{corollary}[Necessity condition for fixation of cooperation.]
  Fixation of cooperation is possible only when
  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
    \begin{aligned}
      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
    \end{aligned}
    \end{equation} 
\end{corollary}
When there is horizontal transmission bias for cooperation, fixation can occured for every value of vertical transmission because $\hat{v}<0$.
However, if the the horizontal bias favours defection, for fixation of cooperation to occur the vertical transmission must be higer than $\hat{v}$.
\\

We already examine the effect of social association in the case of perfect vertical transmission ($v=1$). Now we'll move to the genral case where $0<v\leq 1$.
We denote the social association boundaries of the general case by
\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting_general_case}
  \hat{a}_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
  \hat{a}_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A}.
\end{aligned}\end{equation}
\emph{Corollary~\autoref{corollary:Intermediate_association}} is true for the general but with new boundaries coefficients $\hat{a}_1$, $\hat{a}_2$. \autoref{fig:result3}c and \autoref{fig:result3}d illustrate this result.

@@

\begin{figure}[htb]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
    The vertical transmission rate $v$ is on the x-axis.
    Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines in figures \textbf{(a)}, \textbf{(b)}. 
    Soical association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines in figures \textbf{(c)}, \textbf{(d)}.
    (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
    (\textbf{c}), $b=1.2$, $T_A=0.5$, $T_B = 0.4$, $c=0.5$.
    (\textbf{d}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $c=0.5$.}
    \label{fig:result3}
\end{figure}
